\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template
		
		\bibitem{1}
		Appel, A.,
		\newblock {\em The Notion of Quantitative Invisibility and the Machine Rendering of Solids, } 
		\newblock Proceedings ACM 1967 National Conference.
		
		\bibitem{2}
		Appel, A.,
		\newblock {\em Some Techniques for Shading Machine Renderings of Solids, } 
		\newblock 1968 SJCC, AFIPS Vol. 32.
		
		\bibitem{3}
		Appel, A.,
		\newblock {\em On Calculating the Illusion of Reality, } 
		\newblock IFIP 1968.
		
		\bibitem{4}
		Bouknight, W. J.,
		\newblock {\em A Procedure for the Generation of 3-D Half-Toned Computer Graphics Presentations,} 
		\newblock CACM, Vol. 13, no. 6, Sept. 1970.
		
		\bibitem{5}
		Bouknight, W. J. and Kelley, K.,
		\newblock {\em An Algorithm for Producing Half-Tone Computer Graphics Presentations with Shadows and Moveable Light Sources,} 
		\newblock 1970 SJCC, AFIPS Vol. 36.
		
		\bibitem{6}
		Bui Tuong Phong and Crow, F. C.,
		\newblock {\em Improved Rendition of Polygonal Models of Curved Surfaces,} 
		\newblock Proc. of the 2nd USA-Japan Computer Conf., 1975.
		
		\bibitem{7}
		Clark, J. H.,
		\newblock {\em Hierarchical Geometric Models for Visible Surface Algorithms,} 
		\newblock CACM, Vol. 19 no. 10, Oct. 1976.
		
		\bibitem{8}
		Crow, F. C.,
		\newblock {\em The Aliasing Problem in Computer- Synthesized Shaded Images,} 
		\newblock Dept of Computer Science University of Utah, UTEC-CSc-76-015, March 1976. (abridged version to appear in CACM)
		
		\bibitem{9}
		Newell, M. G., Newell, R. G. and Sancha, T. L.
		\newblock {\em A Solution to the Hidden-Surface Problem,} 
		\newblock Proceedings of the 1972 ACM National Conference.
		
		\bibitem{10}
		Newell, M. G.,
		\newblock {\em The Utilization of Procedural Models in Digital Image Synthesis,} 
		\newblock Department of Computer Science, University of Utah, UTEC-CSc-76-218, Summer 1975.
		
		\bibitem{11}
		Sutherland, I. E.,
		\newblock {\em Polygon Sorting by Subdivision: A Solution to the Hidden-Surface Problem,} 
		\newblock Unpublished, 1973.
		
		\bibitem{12}
		Sutherland, I. E., Sproull, R. F. and Schu- maker, R. G.,
		\newblock {\em A Characterization of Ten Hidden- Surface Algorithms,} 
		\newblock Computing Surveys, Vol. 6, No. 1, March 1974.
		
\end{thebibliography}